---
title: "SSNA 9 Deliverable: Coauthorship Peer Effect in Publications"
author: "Alice (Shuhan Ai)"
output: pdf_document
date: "2022-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
```

# Deliverable 9 Coauthorship Peer Effect in Publications

```{r, echo=TRUE, warning=FALSE, message=FALSE}
rm(list = ls())

#load packages
library(spatialreg)
library(spdep)
library(igraph)
library(classInt)
library(RColorBrewer)
library(splitstackshape)
library(magrittr)

#read table as my datattrout
setwd("~/Data/SSNA")
a<-read.csv("scopus1.csv")

authors<-as.data.frame(a[,1])
colnames(authors)<-"AU"

#split authors name
a1<-cSplit(authors, splitCols = "AU", sep = ",", direction = "wide", drop = FALSE)

#Here we just drop the original first column
a1<-a1[,-1]

#read it as a matrix
mat <- as.matrix(a1)
mat<-tolower(mat)
dim(mat)

#create author-publication two-mode edgelist
a1 <- cbind(a$EID, a1)

mat <- as.matrix(a1)

edgelist_two_mode <- cbind(mat[, 1], c(mat[, -1]))

edgelist_two_mode <- edgelist_two_mode[!is.na(edgelist_two_mode[,2]), ]
g2<- graph.edgelist(edgelist_two_mode[, 2:1], directed = FALSE)  #this is from author to publication

V(g2)$type <- V(g2)$name %in% edgelist_two_mode[ ,2]

mat2 <- t(get.incidence(g2)) #rectangular matix
dim(mat2) #158 human, 56 publications

mat2_to_1<-mat2%*%t(mat2)
dim(mat2_to_1)
summary(diag(mat2_to_1)) 

y<-diag(mat2_to_1)
diag(mat2_to_1) <- 0

#Transforming the matrices to spatial form (row normalized) as shown in following equation 
coauthorship <- mat2_to_1 /rowSums(mat2_to_1)
summary(rowSums(coauthorship))
#9 Na's means there are 9 authors are single authors.

# Replacing potential NA to zeros as shown 
coauthorship[is.na(coauthorship)]<-0
listwCoau<-mat2listw(coauthorship)
summary(rowSums(coauthorship))

#we are allowing the isolated individuals in the weighted list,zero.policy=T
summary(listwCoau, zero.policy=T)
```

## Q1 Test for outcome dependence using author's number of publication as a function of her/his coauthors' number of publications

```{r, echo=TRUE, warning=FALSE, message=FALSE}
moran.test(y,listwCoau, zero.policy=TRUE)
```

Moran I test for the authors' number of publication:Moran I is 0.309 with p value < 0.001, indicating that we have enough evidence to conclude that author's number of publication consistently change with their coauthors' outcomes, either their publications all over the mean or all under the mean.

## Q1 After Removing isolates
```{r, echo=TRUE, warning=FALSE, message=FALSE}
y1 <- data.frame(id=names(y), y=y)
head(y1)

#Q1 After Removing isolates
sub_listNCoau <- subset(listwCoau[[2]], subset=card(listwCoau[[2]])> 0)

#add weights,using style="W" (the normalized version of weights)
sub_listWCoau <- nb2listw(sub_listNCoau, glist=NULL, style="W", zero.policy=NULL) 
#making this a spatial points dataframe
sub_sortAu <- subset(y1, subset=card(listwCoau[[2]]) > 0)
dim(sub_sortAu)

moran.test(sub_sortAu$y,sub_listWCoau, zero.policy=TRUE)
```

After removing the isolated authors, the Moran I is 0.245 with p <0.001, indicating that coauthor's number of publications have impact on author's number of publication. Compared with the above analysis, the Moran I value decreased a little bit.

## Q2 Also visualize this influence level, what may be the mechanism to explain these clusters and outliers?
```{r, echo=TRUE, warning=FALSE, message=FALSE}
mtpubnum <- moran.test(y, listwCoau, zero.policy=TRUE)
label_x = "Author's Number of Publications"
label_y = "Lagged Coauthors' Number of Publications"

mppubnum <- moran.plot(y, listwCoau, zero.policy=T,
                         labels=names(y), xlab = label_x, ylab = label_y)
title(main="Moran’s Plot for the Number of Publication", cex.main=2, col.main="grey11", 
      font.main=2, sub=paste("Plot includes 158 Authors (Moran’s I = ",
                             round(mtpubnum$ estimate[1], 3), ", p < .0001)", sep=""), 
      cex.sub=1.15, col.sub="grey11", font.sub=2,)
```

x axis means author's number of publications, y axis means coauthors' mean number of publication.

As we can see from the above figure, Liu V., Part T. Xu D., Hu S. all in the High-high region, indicating that they and their coauthors all have many publications. Bahr P.R. and McKinney L. are in the High-Low region, suggesting that their own publication numbers outreached their coauthors. For 	
Fairlie R.W., Tandberg D., they are in the Low-high region, which means that even they only have 1 publication in this area, their coauthors have more publications.

## Q3 Test how many higher order neighbors should we account for in this framework?

```{r, echo=TRUE, warning=FALSE, message=FALSE}
plot.spcor(sp.correlogram(sub_listNCoau, sub_sortAu$y, order = 3, method = "I", zero.policy=T), 
        xlab = "Social lags", 
        main = "Social correlogram: Autocorrelation with CIs")
```

As it shown in the plot, we should only account for the first 2 order to in terms of number of publications.

## Q4, Q5 If needed create a higher order weight matrix and test for autocorrelation. Finally, test whether an empty model may be enough to address social dependence.
```{r, echo=TRUE, warning=FALSE, message=FALSE}
PubnumCoau <- spautolm(formula = y ~ 1, data = data.frame(y), 
                       listw = listwCoau)
summary(PubnumCoau)

#Saving the residuals
hNULL<-residuals(PubnumCoau)
summary(hNULL)
#Testing residuals for sp dependence
moran.test(hNULL,listwCoau, zero.policy=TRUE)
```
lambda = 0.209, means this is the average number of publications of coauthors. Since p value < 0.05, the lambda is significant, indicating that 1 more paper coauthor published, the author's publication number will change 0.209 unit under the same direction.
Since the p-value for Moran I test is 0.517 > 0.05, indicating that the residual is i.i.d. Now we can say that the dependence issue addressed with the empty regression coauthorship models in terms of number of publications.
