---
title: "SSNA 9 Deliverable: Coauthorship Peer Effect in Publications"
author: "Alice (Shuhan Ai)"
output: pdf_document
date: "2022-11-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
```

# Deliverable 9 Coauthorship Peer Effect in Publications

```{r, echo=TRUE, warning=FALSE, message=FALSE}
rm(list = ls())

#load packages
library(spatialreg)
library(spdep)
library(igraph)
library(classInt)
library(RColorBrewer)
library(splitstackshape)
library(magrittr)

#read table as my datattrout
setwd("~/Data/SSNA")
a<-read.csv("scopus1.csv")

authors<-as.data.frame(a[,1])
colnames(authors)<-"AU"

#split authors name
a1<-cSplit(authors, splitCols = "AU", sep = ",", direction = "wide", drop = FALSE)

#Here we just drop the original first column
a1<-a1[,-1]

#read it as a matrix
mat <- as.matrix(a1)
mat<-tolower(mat)
dim(mat)

#create author-publication two-mode edgelist
a1 <- cbind(a$EID, a1)

mat <- as.matrix(a1)

edgelist_two_mode <- cbind(mat[, 1], c(mat[, -1]))

edgelist_two_mode <- edgelist_two_mode[!is.na(edgelist_two_mode[,2]), ]
g2<- graph.edgelist(edgelist_two_mode[, 2:1], directed = FALSE)  #this is from author to publication

V(g2)$type <- V(g2)$name %in% edgelist_two_mode[ ,1]

mat2 <- get.incidence(g2) #rectangular matix
dim(mat2) #146 human, 36 publications

mat2_to_1<-mat2%*%t(mat2)

diag(mat2_to_1) <- 0

#Normalize the dataset. Transforming the matrices to spatial form (row normalized) as shown in following equation 
coauthorship <- mat2_to_1 /rowSums(mat2_to_1)
summary(rowSums(coauthorship))
#9 Na's means there are 9 authors are single authors.

# Replacing potential NA to zeros as shown 
coauthorship[is.na(coauthorship)]<-0
listwCoau<-mat2listw(coauthorship)
summary(rowSums(coauthorship))

#we are allowing the isolated individuals in the weighted list,zero.policy=T
summary(listwCoau, zero.policy=T)

#create the number of publication
sortAu <- as.data.frame(sort(degree(g2)[V(g2)$type==F], decreasing =T))
colnames(sortAu) <- c("pubnum")
```

## Q1 Test for outcome dependence using author's number of publication as a function of her/his coauthors' number of publications

```{r, echo=TRUE, warning=FALSE, message=FALSE}
moran.test(sortAu$pubnum,listwCoau, zero.policy=TRUE)
```

Morean test for the authors' number of publication:Moran I is -0.052 with 0.756 p value, indicating that we don't have enought evidence to conclude that author's number of publication will be impacted by their coauthors' outcomes.

## Q1 After Removing isolates
```{r, echo=TRUE, warning=FALSE, message=FALSE}
sub_listNCoau <- subset(listwCoau[[2]], subset=card(listwCoau[[2]])> 0)
sub_listNCoau
summary(sub_listNCoau)
#add weights,using style="W" (the normalized version of weights)
sub_listWCoau <- nb2listw(sub_listNCoau, glist=NULL, style="W", zero.policy=NULL) 
#making this a spatial points dataframe
sub_sortAu <- subset(sortAu, subset=card(listwCoau[[2]]) > 0)
dim(sub_sortAu)

moran.test(sub_sortAu$pubnum,sub_listWCoau, zero.policy=TRUE)
```

Even after removing the isolated authors, the Moran I is -0.055 with 0.77 p value, coauthor's number of publications still don't have impact on author's number of publication.

## Q2 Also visualize this influence level, what may be the mechanism to explain these clusters and outliers?
```{r, echo=TRUE, warning=FALSE, message=FALSE}
mtpubnum <- moran.test(sortAu$pubnum, listwCoau, zero.policy=TRUE)
label_x = "Author's Number of Publications"
label_y = "Lagged Coauthors' Number of Publications"

mppubnum <- moran.plot(sortAu$pubnum, listwCoau, zero.policy=T,
                         labels=sortAu$row.name, xlab = label_x, ylab = label_y)
title(main="Moran’s Plot for the Number of Publication", cex.main=2, col.main="grey11", 
      font.main=2, sub=paste("Plot includes 158 Authors (Moran’s I = ",
                             round(mtpubnum$ estimate[1], 3), ", p < .0001)", sep=""), 
      cex.sub=1.15, col.sub="grey11", font.sub=2,)

```

x axis means author's number of publications, y axis means coauthors' mean number of publication
The dots with label means they may not meaningful under the HH/LH/LL/HL region, they may indicate some special mechanism, but I don't think these explanation meaningful cause the moran test is insignificant.

## Q3 Test how many higher order neighbors should we account for in this framework?

```{r, echo=TRUE, warning=FALSE, message=FALSE}
plot.spcor(sp.correlogram(sub_listNCoau, sub_sortAu$pubnum, order = 3, method = "I", zero.policy=T), 
           xlab = "Social lags", 
           main = "Social correlogram: Autocorrelation with CIs")
```

As it shown in the plot, we should only account for the first order to in terms of number of publications.

## Q4, Q5 If needed create a higher order weight matrix and test for autocorrelation. Finally, test whether an empty model may be enough to address social dependence.
```{r, echo=TRUE, warning=FALSE, message=FALSE}
PubnumCoau <- spautolm(formula = pubnum ~ 1, data = data.frame(sortAu), listw = listwCoau)
summary(PubnumCoau)

#Saving the residuals
hNULL<-residuals(PubnumCoau)
summary(hNULL)
#Testing residuals for sp dependence
moran.test(hNULL,listwCoau, zero.policy=TRUE)
```

Since the p-value for Moran I test is 0.453 > 0.05, indicating that the residual is i.i.d. Now we can say that the dependence issue addressed with the empty regression coauthorship models in terms of number of publications.
